\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-08 k-planar.tex
Note to self

  Assign each vertex $v$ of $N'$ a colour $\alpha(v)\in\{1,2,3\}$ as follows:
  Let $w$ be the first vertex of $F$ encountered on the path in $T$ from $v$ to the root of $T$.  (This implies that $w=v$ for $v\in V(F)$.)  Since $w\in V(F)$, $w\in P_i$ for some $i\in\{1,2,3\}$ and we define $\alpha(v):=i$.

  If $k<3$ then let $\tau:=v_1v_2v_3$ be any inner face of $N'$.  Otherwise, $k=3$, in which case we apply Sperner's Lemma to obtain an inner face $\tau:=v_1v_2v_3$ such that $\alpha(v_i)=i$ for each $i\in\{1,2,3\}$.
  For each $i\in\{1,2,3\}$, let $Q_i$ be the shortest path, in $T$, from $v_i$ to $V(F)$.
   %
   %
   % If $k=3$, set $R_i := P_i$ for each $i\in\{1,2,3\}$.  Otherwise, as in \citep{DJMMUW20}, split $P_1,\ldots,P_k$ to partition $V(F)$ into three sets $R_1$, $R_2$, and $R_3$ such that each $F[R_i]$ is a non-empty path and each $R_i$ contains vertices from exactly one of $P_1,\ldots,P_k$.
  %
	% Next, as in \citep{DJMMUW20}, use Sperner's Lemma to find an inner face $\tau=v_1v_2v_3$ of $N'$ such that, $T$ contains disjoint vertical paths $Q_1,Q_2,Q_3$ such that each $Q_i$ begins at $v_i$, ends at some vertex in $R_i$, and whose internal vertices (if any) are contained in $N'-V(F)$.
	Let $\overline{Y}$ denote the subgraph of $N'$ consisting of vertices and edges of $Q_1$, $Q_2$, $Q_3$, and $\tau$.  Let $\overline{Y}^+$ denote the subgraph of $N$ consisting of the vertices and edges of $\overline{Y}$ plus the vertices and edges of every kite formed by a crossing between an edge of $G$ and an edge of $\overline{Y}$.  Let $Y:= V(\overline{Y}-F)$ and let $Y^+:=V(\overline{Y}^+-F)$.

>>>>

  Assign each vertex $v$ of $N'$ a colour $\alpha(v)\in\{1,2,3\}$ as follows:
  Let $w$ be the first vertex of $F$ encountered on the path in $T$ from $v$ to the root of $T$.  (This implies that $w=v$ when $v$ is a vertex of $F$.)  Since $w\in V(F)$, $w\in P_i$ for some $i\in\{1,2,3\}$ and we define $\alpha(v):=i$.

  If $k<3$ then let $\tau:=v_1v_2v_3$ be any inner face of $N'$.  \note{PM}{Not quite that easy. We want $M$ to be $2$-connected so have to make sure $\overline{Y}$ attaches to at least two different vertices of $F$.}
  Otherwise, $k=3$, in which case we apply Sperner's Lemma to obtain an inner face $\tau:=v_1v_2v_3$ such that $\alpha(v_i)=i$ for each $i\in\{1,2,3\}$.
  For each $i\in\{1,2,3\}$, let $Q_i$ be the shortest path, in $T$, from $v_i$ to $V(F)$.
   %
   %
   % If $k=3$, set $R_i := P_i$ for each $i\in\{1,2,3\}$.  Otherwise, as in \citep{DJMMUW20}, split $P_1,\ldots,P_k$ to partition $V(F)$ into three sets $R_1$, $R_2$, and $R_3$ such that each $F[R_i]$ is a non-empty path and each $R_i$ contains vertices from exactly one of $P_1,\ldots,P_k$.
  %
	% Next, as in \citep{DJMMUW20}, use Sperner's Lemma to find an inner face $\tau=v_1v_2v_3$ of $N'$ such that, $T$ contains disjoint vertical paths $Q_1,Q_2,Q_3$ such that each $Q_i$ begins at $v_i$, ends at some vertex in $R_i$, and whose internal vertices (if any) are contained in $N'-V(F)$.
	Let $\overline{Y}$ denote the subgraph of $N'$ consisting of vertices and edges of $Q_1$, $Q_2$, $Q_3$, and $\tau$.  Let $\overline{Y}^+$ denote the subgraph of $N$ consisting of the vertices and edges of $\overline{Y}$ plus the vertices and edges of every kite formed by a crossing between an edge of $G$ and an edge of $\overline{Y}$.  Let $Y:= V(\overline{Y}-F)$ and let $Y^+:=V(\overline{Y}^+-F)$.
